---
title: "Peaches"
author: "Sarah Christofides"
date: "09/11/2020"
output: html_document
---

#Set up R
##Load libraries
```{r}
library(dplyr)
library(emmeans)
library(gridExtra)
library(ggmosaic)
library(ggplot2)
library(mvabund)
library(multivariMate)
library(MuMIn)
library(ordinal)
library(rcompanion)
library(RVAideMemoire)
library(vegan)
```
##Colours
```{r}
#Colours for peach characteristics
charcol<-c(
  Aroma=rgb(red=255,green=191,blue=127,maxColorValue=255),#light orange
  Sweet=rgb(red=255,green=127,blue=0,maxColorValue=255),#bright orange
  Acid=rgb(red=229,green=25,blue=50,maxColorValue=255),#red
  Bitter=rgb(red=255,green=153,blue=191,maxColorValue=255),#pink
  Astringent=rgb(red=165,green=237,blue=255,maxColorValue=255),#light blue 
  Juicy=rgb(red=25,green=178,blue=255,maxColorValue=255),#bright blue
  Crunchy=rgb(red=178,green=255,blue=140,maxColorValue=255),#light green
  Fibrous=rgb(red=50,green=255,blue=0,maxColorValue=255),#bright green
  Firm=rgb(red=101,green=76,blue=255,maxColorValue=255),#purple
  Soft=rgb(red=204,green=191,blue=255,maxColorValue=255),#lilac
  Mealy=rgb(red=100,green=100,blue=100,maxColorValue=255)#grey
)
#Colours for purchase characteristics
purchasecol<-c(
  Scent=rgb(red=255,green=191,blue=127,maxColorValue=255),#light orange
  Ripeness=rgb(red=255,green=127,blue=0,maxColorValue=255),#bright orange
  Size=rgb(red=229,green=25,blue=50,maxColorValue=255),#red
  Shape=rgb(red=255,green=153,blue=191,maxColorValue=255),#pink
  Blemishes=rgb(red=165,green=237,blue=255,maxColorValue=255),#light blue
  Price=rgb(red=25,green=178,blue=255,maxColorValue=255),#bright blue
  Name=rgb(red=178,green=255,blue=140,maxColorValue=255),#light green
  Texture=rgb(red=50,green=255,blue=0,maxColorValue=255),#bright green
  Colour=rgb(red=101,green=76,blue=255,maxColorValue=255),#purple
  Taste=rgb(red=204,green=191,blue=255,maxColorValue=255),#lilac
  Retailer=rgb(red=0,green=0,blue=0,maxColorValue=255),#black
  BB4=rgb(red=100,green=100,blue=100,maxColorValue=255), #light grey
  Other=rgb(red=50,green=50,blue=50,maxColorValue=255)#dark grey
)
#Colours for person characteristics
personcol<-c(
  Site=rgb(red=229,green=25,blue=50,maxColorValue=255),#red
  Gender=rgb(red=25,green=178,blue=255,maxColorValue=255),#bright blue
  Age=rgb(red=50,green=255,blue=0,maxColorValue=255),#bright green
  Ethnic=rgb(red=204,green=191,blue=255,maxColorValue=255),#lilac
  Frequency=rgb(red=255,green=127,blue=0,maxColorValue=255)#bright orange
)
```
#Prepare data
Based on the Excel sheet 'All data sorted by gender'
```{r}
#Load in data
peach<-read.csv("Peaches study 2019 sensory results inc Italian peach sample sorted agh 311020.csv")

#Look at data structure
str(peach)

#Convert all columns to factors
peach<-as.data.frame(lapply(peach, as.factor))

#Add in the correct names to the factor levels for person characteristics
levels(peach$Site)<-c("CardiffMet", "CardiffUni", "Calabria")
levels(peach$Gender)<-c("Male", "Female", "NA")
levels(peach$Age)<-c("18-29",	"30-39",	"40-49",	"50-59",	"60+",	"NA")
levels(peach$Ethnic)<-c("Caucasian",	"Asian",	"Hispanic",	"Black",	"NativeAmerican",	"Other", "NA")
#Convert "3" to "NA"
peach$Nation<-as.character(peach$Nation)
peach$Nation[peach$Nation=="3"]<-NA
peach$Nation<-as.factor(peach$Nation)

#Add in the correct names to the factor levels for purchase characteristics
levels(peach$Frequency)<-c(">1perWeek",	"Weekly",	"2-3perWeek",	"<1perMonth",	"NA",	">1perMonth")
levels(peach$Name)<-c("Yes", "No", "NA")
peach$If.yes<-as.character(peach$If.yes)
peach$If.yes[peach$If.yes==3]<-NA
#Change value of 11 in Ripeness to 1
peach$Ripeness<-as.factor(gsub("11","1",peach$Ripeness))
for (i in names(peach[,c("Ripeness", "Colour", "Size", "Shape", "Blemishes", "Price", "Aroma", "Texture", "Taste", "Retailer", "BB4", "Other")])){
  levels(peach[,i])<-c("Yes", "No", "NA")
}
#Convert "3" to "NA"
peach$Explanation<-as.character(peach$Explanation)
peach$Explanation[peach$Explanation==3]<-NA

#Convert the ratings back to numeric
peach$Rate.295<-as.numeric(as.character(peach$Rate.295))
peach$Rate.733<-as.numeric(as.character(peach$Rate.733))
peach$Rate.837<-as.numeric(as.character(peach$Rate.837))

#Add in the correct names to the factor levels for peach characteristics
for (i in names(peach[,grep("X[0-9]{3}.[^O]", names(peach))])){
  levels(peach[,i])<-c("Yes", "No")}
#Set "3" to "NA" in the "Other" columns
for (i in names(peach[,grep("X[0-9]{3}.Other", names(peach))])){
  peach[,i]<-as.character(peach[,i])
  peach[,i][peach[,i]==3]<-NA}

#Make sure all NAs are properly coded, then remove unused levels
peach[peach=="NA"]<-NA
peach<-droplevels(peach)

summary(peach)

#Give each respondent a unique ID
peach$Respondent<-seq(1:nrow(peach))

library(tidyr)
#Stack the ratings along with the person and purchase characteristics 
longpeach<-peach[,c(61,1:24)] %>% 
  pivot_longer(cols = c("Rate.837", "Rate.295", "Rate.733"), 
                       names_to = "Treatment", 
                       values_to = "Rating",
                       names_prefix = "Rate.")
#Sort the data by Treatment and respondent ID to make sure it is in the correct order for the next step
longpeach<-longpeach[order(longpeach$Treatment, longpeach$Respondent),]
longpeach$Treatment<-as.factor(longpeach$Treatment)
#Rename the levels
levels(longpeach$Treatment)<-c("Stored1C",	"Fresh",	"Stored5C")

#Add in the peach characteristics
for (i in c("peachy.aroma", "sweet", "acid", "bitter", "astringent", "juicy", "crunchy", "chewy..fibrous.skin", "firm.flesh", "soft.flesh", "mealy..mushy.flesh")){
  longpeach[1:nrow(peach),i]<-peach[,paste0("X295.", i)]
  longpeach[(nrow(peach)+1):(2*nrow(peach)),i]<-peach[,paste0("X733.", i)]
  longpeach[(2*nrow(peach)+1):(3*nrow(peach)),i]<-peach[,paste0("X837.", i)]
}

#Tidy up names
names(longpeach)<-gsub("Aroma","Scent",names(longpeach))
names(longpeach)<-gsub("peachy.aroma","aroma",names(longpeach))
names(longpeach)<-gsub("mealy..mushy.flesh","Mealy",names(longpeach))
names(longpeach)<-gsub(".+\\.{2}","",names(longpeach))
names(longpeach)<-gsub("(.+)\\..+","\\1",names(longpeach))
names(longpeach)<-toTitleCase(names(longpeach))

#Tidy up nationality column
longpeach$Nation<-as.character(longpeach$Nation)
sort(unique(longpeach$Nation))

longpeach$Nation[longpeach$Nation=="Welsh British"]<-"Welsh"
longpeach$Nation[longpeach$Nation=="British Welsh"]<-"Welsh"
longpeach$Nation[longpeach$Nation=="British Scottish"]<-"Scottish"
longpeach$Nation[longpeach$Nation=="British European"]<-"British"
longpeach$Nation[longpeach$Nation=="UK"]<-"British"
longpeach$Nation[longpeach$Nation=="EU"]<-"European"

longpeach$Nation[longpeach$Nation=="KURDISTAN"]<-"Kurdistan"

longpeach$Nation[longpeach$Nation=="Turkey"]<-"Turkish"
longpeach$Nation[longpeach$Nation=="Spain"]<-"Spanish"
longpeach$Nation[longpeach$Nation=="China"]<-"Chinese"
longpeach$Nation[longpeach$Nation=="Italy"]<-"Italian"
longpeach$Nation[longpeach$Nation=="Pakistan" | longpeach$Nation=="Pakastani"]<-"Pakistani"

longpeach$Nation<-as.factor(longpeach$Nation)
summary(longpeach$Nation)

#Add country column
longpeach$Country[longpeach$Site=="Calabria"]<-"Italy"
longpeach$Country[longpeach$Site=="CardiffMet" | longpeach$Site=="CardiffUni"]<-"UK"
longpeach$Country<-as.factor(longpeach$Country)

#Convert to data frame
longpeach<-as.data.frame(longpeach)
#Relevel Treatments and Sites
longpeach$Treatment<-factor(longpeach$Treatment, levels = c("Stored1C",	"Stored5C",	"Fresh"))
longpeach$Site<-relevel(longpeach$Site, ref = "Calabria")

write.csv(longpeach, "longpeach.csv")
```
##Separate out the peach characteristics and convert them to presence/absence
```{r}
PAchars<-longpeach[,25:35]=="Yes"
PAchars<-apply(PAchars, 2, as.numeric)
#Remove any rows with 0 sums
PAchars<-as.data.frame(PAchars)
names(PAchars)<-names(longpeach[,25:35])
```
##Create a dataset with only the person and peach characteristics
```{r}
peachperson<-longpeach[,c(1:7,23:35)]
#Remove rows containing NAs
peachperson<-peachperson[!apply(peachperson,1,function(x)any(is.na(x))),]
#Relevel binomial categories so that No is the reference
for (col in names(peachperson[,10:20])){
  peachperson[,col]<-relevel(peachperson[,col], ref = "No")
}
```
##Collate characteristics which influence decision to purchase
```{r}
#Amalgamate some categories
levels(longpeach$Frequency)
longpeach$Frequency2<-as.character(longpeach$Frequency)
longpeach$Frequency2[longpeach$Frequency2 %in% c("2-3perWeek", ">1perWeek")]<-">1perWeek"
longpeach$Frequency2[longpeach$Frequency2 %in% c("Weekly", ">1perMonth")]<-"WeeklyToMonthly"
longpeach$Frequency2<-factor(longpeach$Frequency2, levels = c("<1perMonth",  "WeeklyToMonthly", ">1perWeek"))

all.purchase<-apply(longpeach[longpeach$Treatment=="Fresh",c(8,10:21)], 2, function(x) sum(x=="Yes", na.rm = T))
all.purchase<-sort(all.purchase, decreasing = T)

purchase<-aggregate(longpeach[longpeach$Treatment=="Fresh",c(8,10:21)], by=list(longpeach$Frequency2[longpeach$Treatment=="Fresh"]), function(x) sum(x=="Yes", na.rm = T))
rownames(purchase)<-purchase[,"Group.1"]
purchase<-purchase[,names(purchase) != "Group.1"]
purchase<-as.matrix(purchase)

purchase.nation<-aggregate(longpeach[longpeach$Treatment=="Fresh",c(8,10:21)], by=list(longpeach$Country[longpeach$Treatment=="Fresh"]), function(x) sum(x=="Yes", na.rm = T))
rownames(purchase.nation)<-purchase.nation[,"Group.1"]
purchase.nation<-purchase.nation[,names(purchase.nation) != "Group.1"]
purchase.nation<-as.matrix(purchase.nation)
```
#Plotting
##Basic plotting
```{r}
plot(longpeach$Rating~longpeach$Treatment)
plot(longpeach$Rating~longpeach$Site)
plot(longpeach$Rating~longpeach$Gender)

plot(longpeach$Juicy~longpeach$Crunchy)
plot(longpeach$Soft~longpeach$Site)
plot(longpeach$Soft~longpeach$Sweet)
plot(longpeach$Soft~longpeach$Firm)
plot(longpeach$Soft~longpeach$Mealy)

```
##NMDS
```{r}
#Create a binomial distance matrix
peachdist<-vegdist(PAchars[rowSums(PAchars)>0,], method = "binomial", binary = T)

##Binomial NMDS. <0.05 is excellent, 0.05-0.1 is very good, 0.1-0.2 is adequate, 0.2 - 0.3 can cause problems, > 0.3 you need to increase the number of dimensions (via 'k=') that you allow the ordination to be carried out in.
#NB This is SLOW for this dataset!
#Didn't converge in 500 runs when k=2. Converged in 20 runs when k=3
nmds1<-metaMDS(peachdist, trymax = 20, k=3, pc="TRUE")

#Colour by site
plot(nmds1$points[,1:2], pch=20, col=longpeach$Site[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,2:3], pch=20, col=longpeach$Site[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,c(1,3)], pch=20, col=longpeach$Site[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
#Colour by Treatment
plot(nmds1$points[,1:2], pch=20, col=longpeach$Treatment[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,2:3], pch=20, col=longpeach$Treatment[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,c(1,3)], pch=20, col=longpeach$Treatment[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
#Colour by gender
plot(nmds1$points[,1:2], pch=20, col=longpeach$Gender[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,2:3], pch=20, col=longpeach$Gender[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,c(1,3)], pch=20, col=longpeach$Gender[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
```
#Purchase characteristics
##Plot purchase characteristics
```{r}
par(mfrow=c(2,2))
barplot(all.purchase, las = 2, main ="All respondents", 
        ylab = "No. affirmative",
        col = purchasecol[
          match(names(all.purchase),names(purchasecol))])
legend("topright", legend = paste("n =", nrow(longpeach[longpeach$Treatment=="Fresh",])), bty="n")
mtext("(A)", side=3, adj=-0.15)
for (i in 1:nrow(purchase)){
  p2<-purchase[i,]
  p2<-sort(p2, decreasing = T)
  barplot(p2, main = rownames(purchase)[i], las=2, 
          ylab = "No. affirmative",
          col = purchasecol[
          match(names(p2),names(purchasecol))])
  legend("topright", legend = paste("n =", nrow(longpeach[longpeach$Treatment=="Fresh" & longpeach$Frequency2 == rownames(purchase)[i],])), bty="n")
  mtext(paste(c("(B)","(C)","(D)")[i]), side=3, adj=-0.15)
}
par(mfrow=c(1,1))
dev.print(pdf,"Results/PurchaseCharacteristics.pdf", height =7, width = 10)

purchase
rowSums(purchase)
```
##mvabund
```{r}
mvpurchase<-mvabund(apply(longpeach[longpeach$Treatment=="Fresh",c(8,10:21)]=="Yes", 2, as.numeric))

purchasemod <- manyglm(mvpurchase ~ longpeach$Frequency2[longpeach$Treatment=="Fresh"], family="binomial")
plot(purchasemod)
purchase.aov<-anova(purchasemod, p.uni="adjusted", pairwise.comp = longpeach$Frequency2[!is.na(rowSums(mvpurchase))])
purchase.aov$table
purchase.aov$pairwise.comp.table
purchase.aov$uni.p[2,]
purchasemod$coefficients

#Plot coefficients with significance indicators
par(mfrow=c(3,5))
for (i in colnames(purchasemod$coefficients)){
plot(c(2,0,-3.5)~c(1,2,3), type = "n",
     xlab = "Frequency of purchase", ylab = "Coefficient", 
     main = i,
     xaxt = "n"); axis(side = 1, at = c(1,2,3), labels = c("Monthly", "Weekly-Monthly", ">1perWeek"))
  if(purchase.aov$uni.p[2,i] <= 0.05 & purchase.aov$uni.p[2,i] >0.01){mtext("*")}
  if(purchase.aov$uni.p[2,i] <= 0.01){mtext("**")}
  lines(purchasemod$coefficients[,i]~c(1,2,3), col = purchasecol[i], lwd = 2)
}
par(mfrow=c(1,1))
dev.print(pdf,"Results/Purchase-mvabund.pdf", height =7, width = 10)

#Write output as table
purchase.tests<-cbind(round(purchase.aov$uni.test,2), round(purchase.aov$uni.p,3))
purchase.tests<-purchase.tests[,order(colnames(purchase.tests))]
purchase.tests<-t(unstack(purchase.tests[-1,], form=purchase.tests[-1,]~colnames(purchase.tests)))
colnames(purchase.tests)<-c("LR", "P.adj")
write.csv(purchase.tests, "Results/PurchaseUnivariateTests.csv")
```
##Chi-squared tests for differences between countries
```{r}
summary(longpeach$Country[longpeach$Treatment=="Fresh"])
155/359
204/359

purchase.chisq<-matrix(NA, nrow=ncol(purchase.nation), ncol=7, dimnames=list(colnames(purchase.nation), c("Total", "Italy", "UK", "ChiSq", "P", "P.adj", "Which")))
for (i in 1:ncol(purchase.nation)){
  cs<-chisq.test(purchase.nation[,i], p=c(0.4317549, 0.5682451))
  purchase.chisq[i,1]<-sum(purchase.nation[,i])
  purchase.chisq[i,2]<-purchase.nation[,i][[1]]
  purchase.chisq[i,3]<-purchase.nation[,i][[2]]
  purchase.chisq[i,4]<-cs[[1]]
  purchase.chisq[i,5]<-cs[[3]]
  purchase.chisq[i,7]<-cs$observed[[1]]-cs$expected[[1]]
}
purchase.chisq<-as.data.frame(purchase.chisq)

purchase.chisq$P.adj<-round(p.adjust(purchase.chisq$P, method = "BH"),3)

purchase.chisq$ChiSq<-round(purchase.chisq$ChiSq, 2)
purchase.chisq$P<-round(purchase.chisq$P, 3)

for (i in 1:nrow(purchase.chisq)){
  if (purchase.chisq$Which[i] < 0 & purchase.chisq$P.adj[i] <=0.05) {purchase.chisq$Nation[i]<-"UK"}
  if (purchase.chisq$Which[i] > 0 & purchase.chisq$P.adj[i] <=0.05) {purchase.chisq$Nation[i]<-"Italy"}
  if (purchase.chisq$P.adj[i] > 0.05) {purchase.chisq$Nation[i]<-"NSD"}
}
purchase.chisq$Which<-NULL

purchase.chisq<-purchase.chisq[order(purchase.chisq$Total, decreasing = T),]
purchase.chisq
```
#Liking rating
##Modelling liking
```{r}
names(longpeach)
qqnorm(longpeach$Rating)

#Based on peach characteristics
mod1<-clmm(as.factor(Rating)~Aroma + Sweet + Acid + Bitter + Astringent + Juicy + Crunchy + Fibrous + Firm + Soft + Mealy + (1|Respondent), data = peachperson, na.action = na.fail)

#peach.model.set<-dredge(mod1)
top.peach.mod<-get.models(peach.model.set, subset = 1)

#Look at only the best models (delta<2)
best.peach.models<-peach.model.set[peach.model.set$delta<2,]
best.peach.models
for (i in 1:nrow(best.peach.models)){
  best.peach.models$Terms[[i]]<-paste0(names(peach.model.set[,2:12])[!is.na(peach.model.set[i,2:12])], collapse = " + ")
}

write.csv(cbind(best.peach.models$Terms, round(best.peach.models[,13:17],2)), "Results/BestPeachModels.csv")

#Get averaged parameters across the whole peach model set
av.mod<-model.avg(peach.model.set)
av.mod$coefficients
av.param<-as.data.frame(confint(av.mod)[-c(1:9),])
av.param$Full<-av.mod$coefficients[1,10:20]

#Based on person characteristics
mod2<-clmm(as.factor(Rating)~Site + Gender + Age + Ethnic + Frequency + (1|Respondent), data = peachperson, na.action = na.fail) #omitted Nation due to singularities

par(mfrow=c(2,2)); plot(mod2); par(mfrow=c(1,1))
person.model.set<-dredge(mod2)

```
##Plot model results
```{r}
#Compare the peach and person model sets
boxplot(peach.model.set$AICc[peach.model.set$delta<6], person.model.set$AICc[person.model.set$delta<6],
        at = c(1,2),
        names = c("Peach", "Person"),
        las = 2,
        ylab = "AICc")

#Plot how many times each predictor occured in the peach acceptable models (delta<6)
n.imp<-apply(peach.model.set[peach.model.set$delta<6,2:12], 2, function(x) sum(x=="+", na.rm = T))

n.imp<-sort(n.imp)
barplot(n.imp, col =  charcol[
          match(names(n.imp),names(charcol))])

#Plot how many times each predictor occured in the person acceptable models (delta<6)
n.imp2<-apply(person.model.set[person.model.set$delta<6,2:6], 2, function(x) sum(x=="+", na.rm = T))
n.imp2<-sort(n.imp2)
barplot(n.imp2, col =  personcol[
          match(names(n.imp2),names(personcol))])

#Combined plot of the rating models
par(mfrow=c(2,2), mar = c(5, 5, 4, 2) + 0.1)
boxplot(peach.model.set$AICc[peach.model.set$delta<6], person.model.set$AICc[person.model.set$delta<6],
        at = c(1,2),
        names = c("Peach", "Person"),
        las = 2,
        ylab = "AICc")
mtext("(A)", side=3, adj=-0.2)
plot.new()
barplot(n.imp, ylab = "No. of occurances", xlab = "Peach characteristics", cex.names = 0.6, las=2,
        col =  charcol[
          match(names(n.imp),names(charcol))])
mtext("(B)", side=3, adj=-0.2)
barplot(n.imp2, ylab = "No. of occurances", xlab = "Person characteristics",
        col =  personcol[
          match(names(n.imp2),names(personcol))])
mtext("(C)", side=3, adj=-0.2)
par(mfrow=c(1,1))
dev.print(pdf,"Results/RatingPredictors.pdf", height =7, width = 10)

#Plot parameter estimates for best peach models
ggplot(data = av.param, aes(x=rownames(av.param), y=Full)) + 
  geom_hline(yintercept = 0, lty=2) +
  geom_point(aes(size=0.5, col = gsub("Yes","",rownames(av.param)))) +
  geom_errorbar(aes(ymin=`2.5 %`, ymax=`97.5 %`, 
                    lwd=0.25, col = gsub("Yes","",rownames(av.param)))) + 
  scale_colour_manual(values=charcol[
    match(gsub("Yes","",rownames(av.param)),names(charcol))]) + 
  theme_bw() + 
  guides(colour = "none", size = "none") +
  scale_x_discrete("Parameters", labels=function(x)gsub("Yes","",x)) +   labs(y="Full model averaged value")
dev.print(pdf,"Results/RatingParameterValues.pdf", height =7, width = 10)
```
##Site and treatment effects
```{r}
#Plot rating by treatment filled by site
ggplot(longpeach, aes(x=Treatment, y=Rating, fill=factor(Site))) + 
  geom_boxplot() + 
  labs(x="Treatment", y="Rating") +
  theme_bw() +
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Site")

#Investigate how similar the treatment ratings are in Calabria
calabria<-longpeach[longpeach$Site=="Calabria",c("Rating", "Treatment","respondent")]
plot(calabria$Rating~calabria$Treatment)
plot(calabria$Rating~calabria$respondent, col = calabria$Treatment)
boxplot(calabria$Rating~calabria$respondent)

#Test the effect of treatment and site
likemod<-clmm(as.factor(Rating)~Site+Treatment+Site:Treatment + (1|Respondent), data = longpeach)

RVAideMemoire::Anova.clmm(likemod, type="II")

#Pairwise comparisons
marginal<-lsmeans(likemod, pairwise ~ Treatment:Site, adjust="tukey") 

marginal

cldList(comparison = as.data.frame(marginal$contrasts)[,"contrast"],
        p.value    = as.data.frame(marginal$contrasts)[,"p.value"],
        threshold  = 0.05)

#Plot rating by site filled by treatment
ggplot(longpeach, aes(x=Site, y=Rating, fill=factor(Treatment))) + 
  geom_boxplot(width=1, coef=0,  outlier.colour="white",
) + 
  geom_violin(alpha=0, scale = "count", width=1, show.legend=F) + 
  labs(x="Site", y="Rating") +
  theme_bw() +
  annotate("text", x = c(0.66,1,1.33, 1.66,2,2.33, 2.63,3,3.33 ), y=10, label = c("ab", "ac", "c", "d", "d", "ab", "bd", "ac", "abc")) + coord_cartesian(clip = 'off') +
  scale_y_continuous(breaks=seq(0,9), limits=c(0,10)) + 
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Treatment")

dev.print(pdf,"Results/RatingSiteTreatment.pdf")
```
#Peach characteristics
##Plotting by site and treatment
```{r}
chartab<-aggregate(PAchars, by=list(longpeach$Site, longpeach$Treatment), sum)
chartab2<-stack(chartab)
chartab2$Site<-rep(chartab$Group.1)
chartab2$Treatment<-rep(chartab$Group.2)

#Plot characteristics by treatment filled by site
ggplot(chartab2, aes(x=Treatment, y=values, fill=factor(Site))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Treatment", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() +
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Site")

#Plot characteristics by site filled by treatment
ggplot(chartab2, aes(x=Site, y=values, fill=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Location", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() +
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Treatment")
dev.print(pdf,"Results/RatingSiteTreatment.pdf", height =7, width = 10)

```
##Tables of characteristics
```{r}
nrow(longpeach[longpeach$Aroma=="Yes",])
nrow(longpeach[longpeach$Aroma=="Yes"&longpeach$Sweet=="Yes",])

makeCharMatrix<-function(data){
  allChars<-matrix("",nrow = ncol(PAchars)-1, ncol = ncol(PAchars)-1, dimnames = list(names(PAchars)[-11],names(PAchars)[-1]))
  charlist<-c("Aroma", "Sweet", "Acid", "Bitter", "Astringent", "Juicy", "Crunchy", "Fibrous", "Firm", "Soft", "Mealy")
  for (i in 1:10){
    for (j in (i+1):11){
      v1<-charlist[i]
      v2<-charlist[j]
      allChars[i,v2]<-nrow(data[data[,v1]=="Yes"&data[,v2]=="Yes",])
    }
  }
  return(allChars)
}

allChars<-makeCharMatrix(longpeach)
CUchars<-makeCharMatrix(longpeach[longpeach$Site=="CardiffUni",])
CMchars<-makeCharMatrix(longpeach[longpeach$Site=="CardiffMet",])
CALchars<-makeCharMatrix(longpeach[longpeach$Site=="Calabria",])

fisher.test(table(longpeach$Aroma, longpeach$Sweet))

```
##Characterictic co-occurrence
```{r}
pairwiseChar<-function(data){
  char.fisher<-matrix(NA, nrow=55, ncol=7, dimnames=list(seq(1, 55), c("Comparison", "Both", "Char1", "Char2", "Neither", "OddsRatio", "P")))
  comps<-vector()
  charlist<-c("Aroma", "Sweet", "Acid", "Bitter", "Astringent", "Juicy", "Crunchy", "Fibrous", "Firm", "Soft", "Mealy")
  for (i in 1:10){
    for (j in (i+1):11){
      if(i == 1 & j == 2){x<-1}
      else {x<-x+1}
      v1<-charlist[i]
      v2<-charlist[j]
      tab<-table(longpeach[,v1], longpeach[,v2])
      fish<-fisher.test(tab)
      comps[[x]]<-paste(v1, "vs", v2)
      char.fisher[x,2]<-tab[[1]]
      char.fisher[x,3]<-tab[[3]]
      char.fisher[x,4]<-tab[[2]]
      char.fisher[x,5]<-tab[[4]]
      char.fisher[x,6]<-fish[[3]]
      char.fisher[x,7]<-fish[[1]]
    }
}

char.fisher<-as.data.frame(char.fisher)
char.fisher$Comparison<-comps
char.fisher$P.adj<-round(p.adjust(char.fisher$P, method = "BH"),3)

char.fisher$OddsRatio<-round(char.fisher$OddsRatio, 2)
char.fisher$P<-round(char.fisher$P, 3)

return(char.fisher)
}

char.fisher<-pairwiseChar(longpeach[,25:35])

char.fisher

write.csv(char.fisher, "Results/CharacterCo-occurrence.csv")

a<-t(as.data.frame(strsplit(char.fisher$Comparison, " vs ")))
b<-graph.edgelist(as.matrix(a), directed = F)
plot(b)
components(b)
```
##Plotting characteristics against each other
```{r}
ggplot(data = longpeach) +
   geom_mosaic(aes(x = product(Sweet,Aroma)),
         fill=c(rgb(1,round(171/1077,1),round(171/1077,1)), #yesyes
                rgb(1,round(97/1077,1),1), #noyes
                rgb(1,round(343/1077,1),1), #yesno
                rgb(round(466/1077,1),round(466/1077,1),1)) #nono
               ) + theme_bw() + 
  geom_text(data = layer_data(last_plot(), 1) %>% filter(.wt > 0),
             aes(x = (xmin + xmax) / 2,
                 y = (ymin + ymax) / 2,
                 label = .wt))

#Plot all pairwise characteristics
plot.pair.chars<-function(data){
plotlist<-list()
charlist<-c("Aroma", "Sweet", "Acid", "Bitter", "Juicy", "Astringent", "Crunchy", "Fibrous", "Firm", "Soft", "Mealy")
for (i in 1:10){
  for (j in (i+1):11){
    v1<-charlist[i]
    v2<-charlist[j]
    #Display tables as %
    tab<-table(data[,c(v1,v2)])/sum(table(data[,c(v1,v2)]))*100
    #Calculate colour codes
    invcol1<-round(tab[1,1]/100,1)+0.25
    invcol2<-round(tab[2,2]/100,1)+0.25
    invcol12<-round(tab[1,2]/100,1)+0.25
    invcol21<-round(tab[2,1]/100,1)+0.25
    collist<-list(invcol1, invcol2, invcol12, invcol21)
    for(num in 1:length(collist)){
      if (collist[[num]] > 1)collist[[num]]<-1
      if (collist[[num]] < 0)collist[[num]]<-0
      }
#    browser()
    plotlist[[paste0(v1,v2)]]<-ggplot(data = data) +
       geom_mosaic(aes(x = syms(c(v2,v1))),
         fill=c(
          rgb(1,1-collist[[1]],1-collist[[1]]), #yesyes
          rgb(1,1-collist[[3]],1), #noyes
          rgb(1,1-collist[[4]],1), #yesno
          rgb(1-collist[[2]],1-collist[[2]],1)) #nono
                   ) +
      geom_text(data = layer_data(last_plot(), 1) %>% filter(.wt > 0),
                 aes(x = (xmin + xmax) / 2,
                     y = (ymin + ymax) / 2,
                     label = round(.wt/sum(.wt)*100)))
    }
  }
return(plotlist)
}

allsite.plotlist<-plot.pair.chars(longpeach)
cardiff.plotlist<-plot.pair.chars(longpeach[longpeach$Site=="CardiffUni",])
met.plotlist<-plot.pair.chars(longpeach[longpeach$Site=="CardiffMet",])
calab.plotlist<-plot.pair.chars(longpeach[longpeach$Site=="Calabria",])

marrangeGrob(allsite.plotlist[names(allsite.plotlist) %in% c("JuicyCrunchy", "SweetSoft", "SweetJuicy", "AromaSweet", "AromaSoft", "AcidBitter")], nrow = 2, ncol = 3, top = NULL)
marrangeGrob(cardiff.plotlist[names(cardiff.plotlist) %in% c("JuicyCrunchy", "SweetSoft", "SweetJuicy", "AromaSweet", "AromaSoft", "AcidBitter")], nrow = 2, ncol = 3, top = NULL)
marrangeGrob(met.plotlist[names(met.plotlist) %in% c("JuicyCrunchy", "SweetSoft", "SweetJuicy", "AromaSweet", "AromaSoft", "AcidBitter")], nrow = 2, ncol = 3, top = NULL)
marrangeGrob(calab.plotlist[names(calab.plotlist) %in% c("JuicyCrunchy", "SweetSoft", "SweetJuicy", "AromaSweet", "AromaSoft", "AcidBitter")], nrow = 2, ncol = 3, top = NULL)

marrangeGrob(allsite.plotlist[names(allsite.plotlist) %in% c("JuicyCrunchy", "SweetSoft", "SweetJuicy", "AromaSweet", "AromaSoft", "AcidBitter")], nrow = 2, ncol = 3, top = NULL)

#Export only the pairs significantly associated
sigPairs<-gsub(" vs ", "", char.fisher[char.fisher$P.adj <= 0.05,1])

pdf("Results/SigPairwiseCharacters.pdf", height = 9, width = 12)
marrangeGrob(lapply(allsite.plotlist[names(allsite.plotlist) %in% sigPairs], ggplotGrob),
             layout_matrix = matrix(seq_len(5*6), nrow = 5, ncol = 6, byrow = T), top = NULL)
dev.off()

pdf("Results/SelectPairwiseCharacters.pdf", height = 9, width = 12)
marrangeGrob(lapply(allsite.plotlist[names(allsite.plotlist) %in% sigPairs[!sigPairs %in% c("AromaBitter", "AromaAstringent", "SweetAcid", "SweetBitter", "SweetAstringent", "CrunchySoft", "CrunchyMealy", "FirmSoft", "FirmMealy", "JuicySoft", "AromaSoft")]], ggplotGrob),
             layout_matrix = matrix(seq_len(4*5), nrow = 4, ncol = 5, byrow = T), top = NULL)
dev.off()

```
##mvabund
```{r}
mvpeach<-mvabund(PAchars)

mvmod <- manyglm(mvpeach ~ longpeach$Site*longpeach$Treatment, family="binomial")
plot(mvmod)
mv.aov<-anova(mvmod, p.uni="adjusted")
mv.aov$table
mvmod$coefficients

uni.tests<-cbind(round(mv.aov$uni.test,2), round(mv.aov$uni.p,3))
colnames(uni.tests)<-c(paste0(colnames(uni.tests)[1:11], ".Dev"),paste0(colnames(uni.tests)[12:22], ".P"))
uni.tests<-uni.tests[,order(colnames(uni.tests))]
write.csv(uni.tests[-1,], "Results/univariateTests.csv")
```
##Plotting based on mvabund
```{r}
facetlist<-list()
#Plot characteristics with significant interaction 
for (i in c("Acid", "Aroma", "Crunchy", "Firm", "Juicy", "Sweet")){
  facetlist[[i]]<-ggplot(chartab2 %>% filter(ind == i),
       aes(x=Site, y=values, fill=factor(Site), alpha=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Location", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() + 
  theme(strip.background = element_rect(fill="#654CFF")) +
  scale_fill_manual(values=c("#FF7F00", "#19B2FF", "#E51932"), guide = "none") +
  scale_alpha_manual(values=c(0.5, 0.75, 1), guide = "none")
}
#Plot characters affected by neither
facetlist[["Astringent"]]<-ggplot(chartab2 %>% filter(ind == "Astringent"),
       aes(x=Site, y=values, fill=factor(Site), alpha=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Location", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() +
  scale_fill_manual(values=c("#FF7F00", "#19B2FF", "#E51932"), guide = "none") +
  scale_alpha_manual(values=c(0.5, 0.75, 1), guide = "none")
#Plot characteristics only affected by site 
for (i in c("Fibrous", "Mealy", "Soft")){
 facetlist[[paste0("S.",i)]]<-ggplot(chartab2 %>% filter(ind == i),
                  aes(x=Site, y=values, fill=factor(Site))) + 
    geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
    labs(x="Location", y="No. affirmative", tab = "(A)") +
    facet_wrap(~ind) + theme_bw() + 
    theme(strip.background = element_rect(fill="#A5EDFF")) +
    scale_fill_manual(values=c("#FF7F00", "#19B2FF", "#E51932"), guide = "none")
}
#Plot characteristics only affected by treatment
for (i in c("Bitter", "Soft")){
 facetlist[[paste0("T.",i)]]<-ggplot(chartab2 %>% filter(ind == i),
                  aes(x=Treatment, y=values, fill=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Treatment", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() + 
  theme(strip.background = element_rect(fill="#FF99BF")) +
  scale_fill_manual(values=c("#A4A4A4", "#6E6E6E", "#424242"), guide = "none")
}

names(facetlist)
pdf("Results/mvabundCharacters.pdf", height = 9, width = 12)
marrangeGrob(facetlist[c(1:6,8:9,11,10,12,7)], nrow = 4, ncol = 3, top = NULL)
dev.off()

```