---
title: "Peaches"
author: "Sarah Christofides"
date: "09/11/2020"
output: html_document
---

#Set up R
##Load libraries
```{r}
library(car)
library(dplyr)
library(dunn.test)
library(emmeans)
library(gridExtra)
library(ggmosaic)
library(ggplot2)
library(igraph)
library(mvabund)
library(multivariMate)
library(MuMIn)
library(ordinal)
library(rcompanion)
library(RVAideMemoire)
library(tidyr)
library(tools)
library(vegan)
```
##Colours
```{r}
#Colours for peach characteristics
charcol<-c(
  Aroma=rgb(red=255,green=191,blue=127,maxColorValue=255),#light orange
  Sweet=rgb(red=255,green=127,blue=0,maxColorValue=255),#bright orange
  Acid=rgb(red=229,green=25,blue=50,maxColorValue=255),#red
  Bitter=rgb(red=255,green=153,blue=191,maxColorValue=255),#pink
  Astringent=rgb(red=165,green=237,blue=255,maxColorValue=255),#light blue 
  Juicy=rgb(red=25,green=178,blue=255,maxColorValue=255),#bright blue
  Crunchy=rgb(red=178,green=255,blue=140,maxColorValue=255),#light green
  Fibrous=rgb(red=50,green=255,blue=0,maxColorValue=255),#bright green
  Firm=rgb(red=101,green=76,blue=255,maxColorValue=255),#purple
  Soft=rgb(red=204,green=191,blue=255,maxColorValue=255),#lilac
  Mealy=rgb(red=100,green=100,blue=100,maxColorValue=255)#grey
)
#Colours for purchase characteristics
purchasecol<-c(
  Scent=rgb(red=255,green=191,blue=127,maxColorValue=255),#light orange
  Ripeness=rgb(red=255,green=127,blue=0,maxColorValue=255),#bright orange
  Size=rgb(red=229,green=25,blue=50,maxColorValue=255),#red
  Shape=rgb(red=255,green=153,blue=191,maxColorValue=255),#pink
  Blemishes=rgb(red=165,green=237,blue=255,maxColorValue=255),#light blue
  Price=rgb(red=25,green=178,blue=255,maxColorValue=255),#bright blue
  Name=rgb(red=178,green=255,blue=140,maxColorValue=255),#light green
  Texture=rgb(red=50,green=255,blue=0,maxColorValue=255),#bright green
  Colour=rgb(red=101,green=76,blue=255,maxColorValue=255),#purple
  Taste=rgb(red=204,green=191,blue=255,maxColorValue=255),#lilac
  Retailer=rgb(red=0,green=0,blue=0,maxColorValue=255),#black
  BB4=rgb(red=100,green=100,blue=100,maxColorValue=255), #light grey
  Other=rgb(red=50,green=50,blue=50,maxColorValue=255)#dark grey
)
#Colours for person characteristics
personcol<-c(
  Site=rgb(red=229,green=25,blue=50,maxColorValue=255),#red
  Gender=rgb(red=25,green=178,blue=255,maxColorValue=255),#bright blue
  Age=rgb(red=50,green=255,blue=0,maxColorValue=255),#bright green
  Ethnic=rgb(red=204,green=191,blue=255,maxColorValue=255),#lilac
  Frequency=rgb(red=255,green=127,blue=0,maxColorValue=255),#bright orange
  Frequency2=rgb(red=255,green=127,blue=0,maxColorValue=255)#bright orange
)
```
#Prepare data
Based on the Excel sheet 'All data sorted by gender'
```{r}
#Load in data
peach<-read.csv("Peaches study 2019 sensory results inc Italian peach sample sorted agh 311020.csv")

#Look at data structure
str(peach)

#Convert all columns to factors
peach<-as.data.frame(lapply(peach, as.factor))

#Add in the correct names to the factor levels for person characteristics
levels(peach$Site)<-c("CF1", "CF2", "IT")
levels(peach$Gender)<-c("Male", "Female", "NA")
levels(peach$Age)<-c("18-29",	"30-39",	"40-49",	"50-59",	"60+",	"NA")
levels(peach$Ethnic)<-c("Caucasian",	"Asian",	"Hispanic",	"Black",	"NativeAmerican",	"Other", "NA")
#Convert "3" to "NA"
peach$Nation<-as.character(peach$Nation)
peach$Nation[peach$Nation=="3"]<-NA
peach$Nation<-as.factor(peach$Nation)

#Add in the correct names to the factor levels for purchase characteristics
levels(peach$Frequency)<-c(">1perWeek",	"Weekly",	"2-3perWeek",	"<1perMonth",	"NA",	">1perMonth")
levels(peach$Name)<-c("Yes", "No", "NA")
peach$If.yes<-as.character(peach$If.yes)
peach$If.yes[peach$If.yes==3]<-NA
#Change value of 11 in Ripeness to 1
peach$Ripeness<-as.factor(gsub("11","1",peach$Ripeness))
for (i in names(peach[,c("Ripeness", "Colour", "Size", "Shape", "Blemishes", "Price", "Aroma", "Texture", "Taste", "Retailer", "BB4", "Other")])){
  levels(peach[,i])<-c("Yes", "No", "NA")
}
#Convert "3" to "NA"
peach$Explanation<-as.character(peach$Explanation)
peach$Explanation[peach$Explanation==3]<-NA

#Convert the ratings back to numeric
peach$Rate.295<-as.numeric(as.character(peach$Rate.295))
peach$Rate.733<-as.numeric(as.character(peach$Rate.733))
peach$Rate.837<-as.numeric(as.character(peach$Rate.837))

#Add in the correct names to the factor levels for peach characteristics
for (i in names(peach[,grep("X[0-9]{3}.[^O]", names(peach))])){
  levels(peach[,i])<-c("Yes", "No")}
#Set "3" to "NA" in the "Other" columns
for (i in names(peach[,grep("X[0-9]{3}.Other", names(peach))])){
  peach[,i]<-as.character(peach[,i])
  peach[,i][peach[,i]==3]<-NA}

#Make sure all NAs are properly coded, then remove unused levels
peach[peach=="NA"]<-NA
peach<-droplevels(peach)

summary(peach)

#Give each respondent a unique ID
peach$Respondent<-seq(1:nrow(peach))

#Stack the ratings along with the person and purchase characteristics 
longpeach<-peach[,c(61,1:24)] %>% 
  pivot_longer(cols = c("Rate.837", "Rate.295", "Rate.733"), 
                       names_to = "Treatment", 
                       values_to = "Rating",
                       names_prefix = "Rate.")
#Sort the data by Treatment and respondent ID to make sure it is in the correct order for the next step
longpeach<-longpeach[order(longpeach$Treatment, longpeach$Respondent),]
longpeach$Treatment<-as.factor(longpeach$Treatment)
#Rename the levels
levels(longpeach$Treatment)<-c("Stored1C",	"Fresh",	"Stored5C")

#Add in the peach characteristics
for (i in c("peachy.aroma", "sweet", "acid", "bitter", "astringent", "juicy", "crunchy", "chewy..fibrous.skin", "firm.flesh", "soft.flesh", "mealy..mushy.flesh")){
  longpeach[1:nrow(peach),i]<-peach[,paste0("X295.", i)]
  longpeach[(nrow(peach)+1):(2*nrow(peach)),i]<-peach[,paste0("X733.", i)]
  longpeach[(2*nrow(peach)+1):(3*nrow(peach)),i]<-peach[,paste0("X837.", i)]
}

#Tidy up names
names(longpeach)<-gsub("Aroma","Scent",names(longpeach))
names(longpeach)<-gsub("peachy.aroma","aroma",names(longpeach))
names(longpeach)<-gsub("mealy..mushy.flesh","Mealy",names(longpeach))
names(longpeach)<-gsub(".+\\.{2}","",names(longpeach))
names(longpeach)<-gsub("(.+)\\..+","\\1",names(longpeach))
names(longpeach)<-toTitleCase(names(longpeach))

#Tidy up nationality column
longpeach$Nation<-as.character(longpeach$Nation)
sort(unique(longpeach$Nation))

longpeach$Nation[longpeach$Nation=="Welsh British"]<-"Welsh"
longpeach$Nation[longpeach$Nation=="British Welsh"]<-"Welsh"
longpeach$Nation[longpeach$Nation=="British Scottish"]<-"Scottish"
longpeach$Nation[longpeach$Nation=="British European"]<-"British"
longpeach$Nation[longpeach$Nation=="UK"]<-"British"
longpeach$Nation[longpeach$Nation=="EU"]<-"European"

longpeach$Nation[longpeach$Nation=="KURDISTAN"]<-"Kurdistan"

longpeach$Nation[longpeach$Nation=="Turkey"]<-"Turkish"
longpeach$Nation[longpeach$Nation=="Spain"]<-"Spanish"
longpeach$Nation[longpeach$Nation=="China"]<-"Chinese"
longpeach$Nation[longpeach$Nation=="Italy"]<-"Italian"
longpeach$Nation[longpeach$Nation=="Pakistan" | longpeach$Nation=="Pakastani"]<-"Pakistani"

longpeach$Nation<-as.factor(longpeach$Nation)
summary(longpeach$Nation)

#Add country column
longpeach$Country<-NA
longpeach$Country[longpeach$Site=="IT"]<-"Italy"
longpeach$Country[longpeach$Site=="CF1" | longpeach$Site=="CF2"]<-"UK"
longpeach$Country<-as.factor(longpeach$Country)

#Convert to data frame
longpeach<-as.data.frame(longpeach)
#Relevel Treatments and Sites
longpeach$Treatment<-factor(longpeach$Treatment, levels = c("Stored1C",	"Stored5C",	"Fresh"))
longpeach$Site<-relevel(longpeach$Site, ref = "IT")

#Amalgamate some frequency of purchase categories
levels(longpeach$Frequency)
longpeach$Frequency2<-as.character(longpeach$Frequency)
longpeach$Frequency2[longpeach$Frequency2 %in% c("2-3perWeek", ">1perWeek")]<-">1perWeek"
longpeach$Frequency2[longpeach$Frequency2 %in% c("Weekly", ">1perMonth")]<-"WeeklyToMonthly"
longpeach$Frequency2<-factor(longpeach$Frequency2, levels = c("<1perMonth",  "WeeklyToMonthly", ">1perWeek"))

write.csv(longpeach, "longpeach.csv")
```
##Separate out the peach characteristics and convert them to presence/absence
```{r}
PAchars<-longpeach[,25:35]=="Yes"
PAchars<-apply(PAchars, 2, as.numeric)
#Remove any rows with 0 sums
PAchars<-as.data.frame(PAchars)
names(PAchars)<-names(longpeach[,25:35])
```
##Create a dataset with only the person and peach characteristics
```{r}
peachperson<-longpeach[,c(1:6,37,23:35)]
#Remove rows containing NAs
peachperson<-peachperson[!apply(peachperson,1,function(x)any(is.na(x))),]
#Relevel binomial categories so that No is the reference
for (col in names(peachperson[,10:20])){
  peachperson[,col]<-relevel(peachperson[,col], ref = "No")
}
```
##Create a dataset with only the purchase characteristics
```{r}
purchasedat<-longpeach[longpeach$Treatment=="Fresh",c(1:22, 36:37)]
```
##Collate characteristics which influence decision to purchase
```{r}
all.purchase<-apply(purchasedat[,c(8,10:21)], 2, function(x) sum(x=="Yes", na.rm = T))
all.purchase<-sort(all.purchase, decreasing = T)

purchase.freq<-aggregate(purchasedat[,c(8,10:21)], by=list(purchasedat$Frequency2), function(x) sum(x=="Yes", na.rm = T))
rownames(purchase.freq)<-purchase.freq[,"Group.1"]
purchase.freq<-purchase.freq[,names(purchase.freq) != "Group.1"]
purchase.freq<-as.matrix(purchase.freq)

purchase.nation<-aggregate(purchasedat[,c(8,10:21)], by=list(purchasedat$Country), function(x) sum(x=="Yes", na.rm = T))
rownames(purchase.nation)<-purchase.nation[,"Group.1"]
purchase.nation<-purchase.nation[,names(purchase.nation) != "Group.1"]
purchase.nation<-as.matrix(purchase.nation)
```
#Plotting
##Basic plotting
```{r}
plot(longpeach$Rating~longpeach$Treatment)
plot(longpeach$Rating~longpeach$Site)
plot(longpeach$Rating~longpeach$Gender)

plot(longpeach$Juicy~longpeach$Crunchy)
plot(longpeach$Soft~longpeach$Site)
plot(longpeach$Soft~longpeach$Sweet)
plot(longpeach$Soft~longpeach$Firm)
plot(longpeach$Soft~longpeach$Mealy)

```
##NMDS
```{r}
#Create a binomial distance matrix
peachdist<-vegdist(PAchars[rowSums(PAchars)>0,], method = "binomial", binary = T)

##Binomial NMDS. <0.05 is excellent, 0.05-0.1 is very good, 0.1-0.2 is adequate, 0.2 - 0.3 can cause problems, > 0.3 you need to increase the number of dimensions (via 'k=') that you allow the ordination to be carried out in.
#NB This is SLOW for this dataset!
#Didn't converge in 500 runs when k=2. Converged in 20 runs when k=3
nmds1<-metaMDS(peachdist, trymax = 20, k=3, pc="TRUE")

#Colour by site
plot(nmds1$points[,1:2], pch=20, col=longpeach$Site[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
legend("bottomright", levels(longpeach$Site), pch=20, bty="n", col=1:3)
#Colour by Treatment
plot(nmds1$points[,2:3], pch=20, col=longpeach$Treatment[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
legend("bottomright", levels(longpeach$Treatment), pch=20, bty="n", col=1:3)
#Colour by gender
plot(nmds1$points[,1:2], pch=20, col=longpeach$Gender[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,2:3], pch=20, col=longpeach$Gender[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
plot(nmds1$points[,c(1,3)], pch=20, col=longpeach$Gender[rowSums(PAchars)>0], xlab="NMDS1", ylab="NMDS2")
```
#Purchase characteristics
##Plot purchase characteristics
```{r}
par(mfrow=c(1,2))
for (i in 1:nrow(purchase.nation)){
  p2<-purchase.nation[i,]
  p2<-sort(p2, decreasing = T)
  barplot(p2, main = rownames(purchase.nation)[i], las=2, 
          ylab = "No. affirmative",
          col = purchasecol[
          match(names(p2),colnames(purchase.nation))])
  legend("topright", legend = paste("n =", nrow(longpeach[longpeach$Treatment=="Fresh" & longpeach$Frequency2 == rownames(purchase.nation)[i],])), bty="n")
}
par(mfrow=c(1,1))


par(mfrow=c(2,2))
barplot(all.purchase, las = 2, main ="All respondents", 
        ylab = "No. affirmative",
        col = purchasecol[
          match(names(all.purchase),names(purchasecol))])
legend("topright", legend = paste("n =", nrow(longpeach[longpeach$Treatment=="Fresh",])), bty="n")
mtext("(A)", side=3, adj=-0.15)
for (i in 1:nrow(purchase.freq)){
  p2<-purchase.freq[i,]
  p2<-sort(p2, decreasing = T)
  barplot(p2, main = rownames(purchase.freq)[i], las=2, 
          ylab = "No. affirmative",
          col = purchasecol[
          match(names(p2),names(purchasecol))])
  legend("topright", legend = paste("n =", nrow(longpeach[longpeach$Treatment=="Fresh" & longpeach$Frequency2 == rownames(purchase.freq)[i],])), bty="n")
  mtext(paste(c("(B)","(C)","(D)")[i]), side=3, adj=-0.15)
}
par(mfrow=c(1,1))
#dev.print(pdf,"Results/PurchaseCharacteristics.pdf", height =7, width = 10)

plot(Frequency2~Country, data=longpeach[longpeach$Treatment=="Fresh",])

```
##mvabund
```{r}
mvpurchase<-mvabund(apply(purchasedat[!is.na(purchasedat$Frequency2),c(8,10:21)]=="Yes", 2, as.numeric))
purchasemet<-purchasedat[!is.na(purchasedat$Frequency2),c("Country", "Frequency2")]
purchasemet<-purchasemet[!is.na(rowSums(mvpurchase)),]
mvpurchase<-mvpurchase[!is.na(rowSums(mvpurchase)),]

#Assess effect of nation whilst controlling for frequency
nat.purchasemod <- manyglm(mvpurchase ~ Frequency2 * Country, data=purchasemet, family="binomial")

plot(nat.purchasemod)
nat.purchase.aov<-anova(nat.purchasemod, p.uni="adjusted")

#No significant interaction
nat.purchase.aov$table

#Look at individual characters
nat.purchase.aov$uni.p[-1,]

#Assess effect of frequency whilst controlling for nation
freq.purchasemod <- manyglm(mvpurchase ~ Country * Frequency2, data=purchasemet, family="binomial")

freq.purchase.aov<-anova(freq.purchasemod, p.uni="adjusted", pairwise.comp = purchasemet$Frequency2)

freq.purchase.aov$table

freq.purchase.aov$pairwise.comp.table
freq.purchase.aov$uni.p[-1,]

#Write output as table
purchase.tests<-freq.purchase.aov$uni.p
purchase.tests[2,]<-nat.purchase.aov$uni.p[3,]
purchase.tests<-cbind(round(freq.purchase.aov$uni.test,2),
                      round(purchase.tests,3))
purchase.tests<-purchase.tests[,order(colnames(purchase.tests))]
rownames(purchase.tests)<-gsub("2", "", rownames(purchase.tests))
colnames(purchase.tests)<-paste0(c("LR.", "P."), colnames(purchase.tests))
write.csv(purchase.tests[-1,], "Results/PurchaseUnivariateTests.csv")
```
###Obtain model predictions
```{r}
newdat<-data.frame(Country=rep(c("Italy", "UK"), each=3), Frequency2=rep(c("<1perMonth", "WeeklyToMonthly", ">1perWeek"), 2))

purchase.predict<-predict(nat.purchasemod, newdat, type = "response", se.fit = T)
purchase.predict$fit<-as.data.frame(purchase.predict$fit)
purchase.predict$se.fit<-as.data.frame(purchase.predict$se.fit)
purchase.predict$stack<-cbind(newdat, stack(purchase.predict$fit), stack(purchase.predict$se.fit))
names(purchase.predict$stack)<-c("Country", "Frequency", "fitted", "char", "se", "v1")

purchase.predict$byNat<-aggregate(purchase.predict$stack$fitted, list(purchase.predict$stack$Country, purchase.predict$stack$char), mean)
purchase.predict$byNat$x<-purchase.predict$byNat$x*100
names(purchase.predict$byNat)<-c("nation", "char", "percent")

purchase.predict$byFreq<-aggregate(purchase.predict$stack$fitted, list(purchase.predict$stack$Frequency, purchase.predict$stack$char), mean)
purchase.predict$byFreq$x<-purchase.predict$byFreq$x*100
names(purchase.predict$byFreq)<-c("freq", "char", "percent")
purchase.predict$byFreq$freq<-factor(purchase.predict$byFreq$freq, levels=c("<1perMonth", "WeeklyToMonthly", ">1perWeek"))
```
##Plot based on mvabund
###Differences between nations
```{r}
summary(purchasedat$Country[!is.na(purchasedat$Frequency2)])

purchase.nation.percent<-data.frame(percent=rep(NA, 26))
purchase.nation.percent$percent<-c(round(purchase.nation[1,]/111*100, digits=0),
round(purchase.nation[2,]/204*100, digits=0))
purchase.nation.percent$char<-rep(colnames(purchase.nation),  2)
purchase.nation.percent$nation<-rep(rownames(purchase.nation), each=13)

nat.purchase.aov$uni.p[3,]

purchase.plot1<-ggplot(purchase.nation.percent, aes(x=reorder(char, -percent), y=percent, fill=nation)) +
  #Real data
  geom_col(position=position_dodge()) +
  #Model predictions
  geom_col(data=purchase.predict$byNat, aes(alpha=0.25), colour="#555555",  position=position_dodge(), show.legend = F) +
  #Real data outlines
  geom_col(position=position_dodge(), colour="black", alpha=0, show.legend = F) +
  labs(x="Character", y="% affirmative") +
  scale_fill_manual(values=c("#32FF00", "#19B2FF"),"Nation") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.8)) +
  annotate("text", x = c(1,4,5,6,7,8,10), y=c(82, 43, 47, 42, 32, 33, 24), label = "*") +
  coord_cartesian(clip = 'off') +
  geom_text(aes(label = "(A)", x = Inf, y = 85), hjust = -1)
```
###Differences between frequences
```{r}
summary(purchasedat$Frequency2[!is.na(purchasedat$Frequency2)])

purchase.freq.percent<-data.frame(percent=rep(NA, 39))
purchase.freq.percent$percent<-c(round(purchase.freq[1,]/115*100, digits=0),
  round(purchase.freq[2,]/74*100, digits=0),
  round(purchase.freq[3,]/126*100, digits=0))
purchase.freq.percent$char<-rep(colnames(purchase.freq),  3)
purchase.freq.percent$freq<-as.factor(rep(rownames(purchase.freq), each=13))
purchase.freq.percent$freq<-factor(purchase.freq.percent$freq, levels=c("<1perMonth", "WeeklyToMonthly", ">1perWeek"))

freq.purchase.aov$uni.p[3,]

purchase.plot2<-ggplot(purchase.freq.percent, aes(x=reorder(char, -percent), y=percent, fill=freq)) +
  #Real data
  geom_col(position=position_dodge(), colour="black") +
  #Model predictions
  geom_col(data=purchase.predict$byFreq, aes(alpha=0.25), colour="#555555",  position=position_dodge(), show.legend = F) +
  #Real data outlines
  geom_col(position=position_dodge(), colour="black", alpha=0, show.legend = F) +
  labs(x="Character", y="% affirmative") +
  scale_fill_manual(values=c("#FFBF7F", "#FF99BF", "#E51932"),"Frequency") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.8)) +
  coord_cartesian(clip = 'off') +
  geom_text(aes(label = "(B)", x = Inf, y = 72), hjust = -1)

#Plot frequency against country
freqBycountry<-aggregate(purchasedat$Frequency2, list(purchasedat$Frequency2, purchasedat$Country), length)
names(freqBycountry)<-c("Freq", "Country", "No")
freqBycountry$No[1:3]<-freqBycountry$No[1:3]/111*100
freqBycountry$No[4:6]<-freqBycountry$No[4:6]/204*100
purchase.plot3<-ggplot(freqBycountry, aes(x=Country, y=No, fill=Freq)) +
  geom_col() +
  scale_fill_manual(values=c("#FFBF7F", "#FF99BF", "#E51932"),"Frequency") +
  labs(x="Country", y="Percent") +
  theme_bw() +
  coord_cartesian(clip = 'off') +
  geom_text(aes(label = "(C)", x = Inf, y = 97), hjust = -1)

chisq.test(purchasedat$Frequency2, purchasedat$Country)

multiplot(purchase.plot1, purchase.plot3, purchase.plot2, cols = 2)
dev.print(pdf, "./Results/PurchaseCharacteristics.pdf", height=8, width=10)
dev.print(png, "./Results/Fig2.png", height=8, width=10, units="in", res=500)
```
#Liking rating
##Modelling liking
```{r}
names(longpeach)
qqnorm(longpeach$Rating)

#Based on peach characteristics
mod1<-clmm(as.factor(Rating)~Aroma + Sweet + Acid + Bitter + Astringent + Juicy + Crunchy + Fibrous + Firm + Soft + Mealy + (1|Respondent), data = peachperson, na.action = na.fail)

#Get the full model set and export it (as it takes a long time to run)
#peach.model.set<-dredge(mod1)
#saveRDS(peach.model.set, "peach.model.set.Rdata")
peach.model.set<-readRDS("peach.model.set.Rdata")

#Look at only the best models (delta<2)
best.peach.models<-peach.model.set[peach.model.set$delta<2,]
best.peach.models
for (i in 1:nrow(best.peach.models)){
  best.peach.models$Terms[[i]]<-paste0(names(peach.model.set[,2:12])[!is.na(peach.model.set[i,2:12])], collapse = " + ")
}

write.csv(cbind(best.peach.models$Terms, round(best.peach.models[,13:17],2)), "Results/BestPeachModels.csv")

#Get averaged parameters across the whole peach model set
av.mod<-model.avg(peach.model.set)
av.mod$coefficients
av.param<-as.data.frame(confint(av.mod)[-c(1:9),])
av.param$Full<-av.mod$coefficients[1,10:20]

#Based on person characteristics
mod2<-clmm(as.factor(Rating)~Site + Gender + Age + Ethnic + Frequency2 + (1|Respondent), data = peachperson, na.action = na.fail) #omitted Nation due to singularities

par(mfrow=c(2,2)); plot(mod2); par(mfrow=c(1,1))
person.model.set<-dredge(mod2)

```
##Plot model results
```{r}
#Compare the peach and person model sets
boxplot(peach.model.set$AICc[peach.model.set$delta<6], person.model.set$AICc[person.model.set$delta<6],
        at = c(1,2),
        names = c("Peach", "Person"),
        las = 2,
        ylab = "AICc")

#Plot how many times each predictor occured in the peach acceptable models (delta<6)
n.imp<-apply(peach.model.set[peach.model.set$delta<6,2:12], 2, function(x) sum(x=="+", na.rm = T))

n.imp<-sort(n.imp)
barplot(n.imp, col =  charcol[
          match(names(n.imp),names(charcol))])

#Plot how many times each predictor occured in the person acceptable models (delta<6)
n.imp2<-apply(person.model.set[person.model.set$delta<6,2:6], 2, function(x) sum(x=="+", na.rm = T))
n.imp2<-sort(n.imp2)
barplot(n.imp2, col =  personcol[
          match(names(n.imp2),names(personcol))])

#Combined plot of the rating models
par(mfrow=c(2,2), mar = c(7, 5, 1, 2) + 0.1)
boxplot(peach.model.set$AICc[peach.model.set$delta<6], person.model.set$AICc[person.model.set$delta<6],
        at = c(1,2),
        names = c("Peach", "Person"),
        las = 1,
        ylab = "AICc")
mtext("(A)", side=3, adj=-0.2)
plot.new()
barplot(n.imp, ylab = "No. of occurances", xlab = "", cex.names = 0.8, las=2,
        col =  charcol[
          match(names(n.imp),names(charcol))])
title(xlab="Peach characteristics", line=5)
mtext("(B)", side=3, adj=-0.2)
barplot(n.imp2, ylab = "No. of occurances", xlab = "",
        col =  personcol[
          match(names(n.imp2),names(personcol))])
title(xlab="Person characteristics", line=5)
mtext("(C)", side=3, adj=-0.2)
par(mfrow=c(1,1), mar = c(5, 5, 4, 2) + 0.1)

dev.print(pdf,"Results/RatingPredictors.pdf", height =7, width = 10)
dev.print(png, "./Results/Fig4.png", height=7, width=10, units="in", res=500)

#Plot parameter estimates for best peach models
ggplot(data = av.param, aes(x=rownames(av.param), y=Full)) + 
  geom_hline(yintercept = 0, lty=2) +
  geom_point(aes(size=0.5, col = gsub("Yes","",rownames(av.param)))) +
  geom_errorbar(aes(ymin=`2.5 %`, ymax=`97.5 %`, 
                    lwd=0.25, col = gsub("Yes","",rownames(av.param)))) + 
  scale_colour_manual(values=charcol[
    match(gsub("Yes","",rownames(av.param)),names(charcol))]) + 
  theme_bw() + 
  guides(colour = "none", size = "none") +
  scale_x_discrete("Parameters", labels=function(x)gsub("Yes","",x)) +   labs(y="Full model averaged value")

dev.print(pdf,"Results/RatingParameterValues.pdf", height =7, width = 10)
dev.print(png, "./Results/Fig5.png", height=7, width=10, units="in", res=500)

```
##Site and treatment effects
```{r}
#Plot rating by treatment filled by site
ggplot(longpeach, aes(x=Treatment, y=Rating, fill=factor(Site))) + 
  geom_boxplot() + 
  labs(x="Treatment", y="Rating") +
  theme_bw() +
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Site")

#Investigate how similar the treatment ratings are in Calabria
siteIT<-longpeach[longpeach$Site=="IT",c("Rating", "Treatment","Respondent")]
plot(siteIT$Rating~siteIT$Treatment)
plot(siteIT$Rating~siteIT$Respondent, col = siteIT$Treatment)
boxplot(siteIT$Rating~siteIT$Respondent)

#Test the effect of treatment and site
likemod<-clmm(as.factor(Rating)~Site+Treatment+Site:Treatment + (1|Respondent), data = longpeach)

RVAideMemoire::Anova.clmm(likemod, type="II")

#Pairwise comparisons
marginal<-lsmeans(likemod, pairwise ~ Treatment:Site, adjust="tukey") 

marginal

cldList(comparison = as.data.frame(marginal$contrasts)[,"contrast"],
        p.value    = as.data.frame(marginal$contrasts)[,"p.value"],
        threshold  = 0.05)

#Plot rating by site filled by treatment
ggplot(longpeach, aes(x=Site, y=Rating, fill=factor(Treatment))) + 
  geom_boxplot(width=1, coef=0,  outlier.colour="white",
) + 
  geom_violin(alpha=0.5, scale = "count", width=1, show.legend=F) + 
  labs(x="Site", y="Rating") +
  theme_bw() +
  annotate("text", x = c(0.66,1,1.33, 1.66,2,2.33, 2.63,3,3.33 ), y=10, label = c("ab", "ac", "c", "d", "d", "ab", "bd", "ac", "abc")) + coord_cartesian(clip = 'off') +
  scale_y_continuous(breaks=seq(0,9), limits=c(0,10)) + 
  scale_fill_manual(values=c("#A5EDFF", "#19B2FF", "#B2FF8C"),"Treatment")

dev.print(pdf,"Results/RatingSiteTreatment.pdf")
dev.print(png, "./Results/Fig3.png", height=8, width=10, units="in", res=500)

```
#Peach characteristics
##Plotting by site and treatment
```{r}
chartab<-aggregate(PAchars, by=list(longpeach$Site, longpeach$Treatment), sum)
chartab2<-stack(chartab)
chartab2$Site<-rep(chartab$Group.1)
chartab2$Treatment<-rep(chartab$Group.2)

#Plot characteristics by treatment filled by site
ggplot(chartab2, aes(x=Treatment, y=values, fill=factor(Site))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Treatment", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() +
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Site")

#Plot characteristics by site filled by treatment
ggplot(chartab2, aes(x=Site, y=values, fill=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Location", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() +
  scale_fill_manual(values=c("#424242", "#6E6E6E", "#A4A4A4"),"Treatment")
```
##Tables of characteristics
```{r}
nrow(longpeach[longpeach$Aroma=="Yes",])
nrow(longpeach[longpeach$Aroma=="Yes"&longpeach$Sweet=="Yes",])

makeCharMatrix<-function(data){
  allChars<-matrix("",nrow = ncol(PAchars)-1, ncol = ncol(PAchars)-1, dimnames = list(names(PAchars)[-11],names(PAchars)[-1]))
  charlist<-c("Aroma", "Sweet", "Acid", "Bitter", "Astringent", "Juicy", "Crunchy", "Fibrous", "Firm", "Soft", "Mealy")
  for (i in 1:10){
    for (j in (i+1):11){
      v1<-charlist[i]
      v2<-charlist[j]
      allChars[i,v2]<-nrow(data[data[,v1]=="Yes"&data[,v2]=="Yes",])
    }
  }
  return(allChars)
}

allChars<-makeCharMatrix(longpeach)
C1chars<-makeCharMatrix(longpeach[longpeach$Site=="CF1",])
C2chars<-makeCharMatrix(longpeach[longpeach$Site=="CF2",])
ITchars<-makeCharMatrix(longpeach[longpeach$Site=="IT",])

fisher.test(table(longpeach$Aroma, longpeach$Sweet))
```
##Characteristic co-occurrence
```{r}
pairwiseChar<-function(data){
  char.fisher<-matrix(NA, nrow=55, ncol=7, dimnames=list(seq(1, 55), c("Comparison", "Both", "Char1", "Char2", "Neither", "OddsRatio", "P")))
  comps<-vector()
  charlist<-c("Aroma", "Sweet", "Acid", "Bitter", "Astringent", "Juicy", "Crunchy", "Fibrous", "Firm", "Soft", "Mealy")
  for (i in 1:10){
    for (j in (i+1):11){
      if(i == 1 & j == 2){x<-1}
      else {x<-x+1}
      v1<-charlist[i]
      v2<-charlist[j]
      tab<-table(data[,v1], data[,v2])
      fish<-fisher.test(tab)
      comps[[x]]<-paste(v1, "vs", v2)
      char.fisher[x,2]<-tab[[1]]
      char.fisher[x,3]<-tab[[3]]
      char.fisher[x,4]<-tab[[2]]
      char.fisher[x,5]<-tab[[4]]
      char.fisher[x,6]<-fish[[3]]
      char.fisher[x,7]<-fish[[1]]
    }
}

char.fisher<-as.data.frame(char.fisher)
char.fisher$Comparison<-comps
char.fisher$P.adj<-round(p.adjust(char.fisher$P, method = "BH"),3)

char.fisher$OddsRatio<-round(char.fisher$OddsRatio, 2)
char.fisher$P<-round(char.fisher$P, 3)

return(char.fisher)
}

char.fisher<-pairwiseChar(longpeach[,25:35])

char.fisher

write.csv(char.fisher, "Results/CharacterCo-occurrence.csv")

it.char.fisher<-pairwiseChar(longpeach[longpeach$Site=="IT",25:35])
c1.char.fisher<-pairwiseChar(longpeach[longpeach$Site=="CF1",25:35])
c2.char.fisher<-pairwiseChar(longpeach[longpeach$Site=="CF2",25:35])
```
##Plotting characteristics against each other
```{r}
makecharnetwk<-function(fisher.result, sig.only=FALSE){
  if(sig.only==TRUE){
    sig.chars<-fisher.result[fisher.result$P.adj<=0.05,]
  }
  else {
  sig.chars<-fisher.result
  }
  
  sig.chars.nodes<-cbind(gsub("(.+) vs.+", "\\1", sig.chars$Comparison), gsub(".+vs (.+)", "\\1", sig.chars$Comparison))
  
  char.netwk<-graph_from_edgelist(sig.chars.nodes, directed = F)

  #Color of nodes based on averaged model coefficients
  red<-(av.param$Full/max(abs(av.param$Full)))[match(names(V(char.netwk)), gsub("Yes","",rownames(av.param)))]
  red[red<0]<-0
  blue<-(av.param$Full/max(abs(av.param$Full)))[match(names(V(char.netwk)), gsub("Yes","",rownames(av.param)))]
  blue[blue>0]<-0
  blue<-blue*-1
  V(char.netwk)$color<-rgb(1-blue, 1-(blue+red), 1-red)
  
  #Size of nodes based on degree
  V(char.netwk)$size<-degree(char.netwk)*1.5#5+15/diff(range(degree(char.netwk)))*degree(char.netwk)
  
  V(char.netwk)$label.color<-"black"
  
  #Colour of edges based on direction of association
  E(char.netwk)[sig.chars$OddsRatio>1]$color<-"red"
  E(char.netwk)[sig.chars$OddsRatio<1]$color<-"#0000AA"

  E(char.netwk)$lty<-1
  E(char.netwk)[sig.chars$P.adj>0.05]$lty<-3
  
  #Size of edges based on significance
  E(char.netwk)$width<-1/((sig.chars$P.adj+0.001)*100)
  #Size of edges based on strength of association
#  E(char.netwk)[sig.chars$OddsRatio>1]$width<-(sig.chars$OddsRatio-1)*10
#  E(char.netwk)[sig.chars$OddsRatio<=1]$width<-sig.chars$OddsRatio*10
  return(char.netwk)
}

all.char.netwk<-makecharnetwk(char.fisher, sig.only = TRUE)
V(all.char.netwk)$label.dist<-c(2.5,1.5,2,1.5,1.5,2.5,1.5,1.5,1.5,2.5,2.5)
V(all.char.netwk)$label.degree<-c(0,-pi/2,0,pi/2,-pi/2,pi,pi/2,-pi/2,-pi/2,pi,pi)

#tk1<-tkplot(char.netwk)
#coord<-tk_coords(tk1)
coord<-readRDS("char.ntwk.coord.Rdata")

plot(all.char.netwk, layout=coord)

dev.print(pdf, "./Results/sig-char-pairs.pdf", height=6, width=6)
dev.print(png, "./Results/Fig6.png", height=6, width=6, units="in", res=500)

max_cliques(char.netwk)

c1.char.ntwk<-makecharnetwk(c1.char.fisher, sig.only = TRUE)
c2.char.ntwk<-makecharnetwk(c2.char.fisher, sig.only = TRUE)
it.char.ntwk<-makecharnetwk(it.char.fisher, sig.only = TRUE)

par(mfrow=c(2,2))
plot(all.char.netwk, layout=coord, main="All")
plot(it.char.ntwk, layout=coord[match(names(V(it.char.ntwk)),names(V(all.char.netwk))),], main="Site IT")
plot(c1.char.ntwk, layout=coord[match(names(V(c1.char.ntwk)),names(V(all.char.netwk))),], main="Site CF1")
plot(c2.char.ntwk, layout=coord[match(names(V(c2.char.ntwk)),names(V(all.char.netwk))),], main="Site CF2")
par(mfrow=c(1,1))

rbind(char.fisher[9,], c1.char.fisher[9,], c2.char.fisher[9,], it.char.fisher[9,])
```
##mvabund
```{r}
mvpeach<-mvabund(PAchars)

mvmod <- manyglm(mvpeach ~ longpeach$Site*longpeach$Treatment, family="binomial")
plot(mvmod)
mv.aov<-anova(mvmod, p.uni="adjusted")
mv.aov$table
mvmod$coefficients

uni.tests<-cbind(round(mv.aov$uni.test,2), round(mv.aov$uni.p,3))
colnames(uni.tests)<-c(paste0(colnames(uni.tests)[1:11], ".Dev"),paste0(colnames(uni.tests)[12:22], ".P"))
uni.tests<-uni.tests[,order(colnames(uni.tests))]
write.csv(uni.tests[-1,], "Results/univariateTests.csv")

gender.check <- manyglm(mvpeach ~ longpeach$Gender, family="binomial")
plot(gender.check)
gen.aov<-anova(gender.check, p.uni="adjusted")
```
##Plotting based on mvabund
```{r}
facetlist<-list()
#Plot characteristics with significant interaction 
for (i in c("Acid", "Aroma", "Crunchy", "Firm", "Juicy", "Sweet")){
  facetlist[[i]]<-ggplot(chartab2 %>% filter(ind == i),
       aes(x=Site, y=values, fill=factor(Site), alpha=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Location", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() + 
  theme(strip.background = element_rect(fill="#654CFF")) +
  scale_fill_manual(values=c("#FF7F00", "#19B2FF", "#E51932"), guide = "none") +
  scale_alpha_manual(values=c(0.5, 0.75, 1), guide = "none")
}
#Plot characters affected by neither
facetlist[["Astringent"]]<-ggplot(chartab2 %>% filter(ind == "Astringent"),
       aes(x=Site, y=values, fill=factor(Site), alpha=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Location", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() +
  scale_fill_manual(values=c("#FF7F00", "#19B2FF", "#E51932"), guide = "none") +
  scale_alpha_manual(values=c(0.5, 0.75, 1), guide = "none")
#Plot characteristics only affected by site 
for (i in c("Fibrous", "Mealy", "Soft")){
 facetlist[[paste0("S.",i)]]<-ggplot(chartab2 %>% filter(ind == i),
                  aes(x=Site, y=values, fill=factor(Site))) + 
    geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
    labs(x="Location", y="No. affirmative", tab = "(A)") +
    facet_wrap(~ind) + theme_bw() + 
    theme(strip.background = element_rect(fill="#A5EDFF")) +
    scale_fill_manual(values=c("#FF7F00", "#19B2FF", "#E51932"), guide = "none")
}
#Plot characteristics only affected by treatment
for (i in c("Bitter", "Soft")){
 facetlist[[paste0("T.",i)]]<-ggplot(chartab2 %>% filter(ind == i),
                  aes(x=Treatment, y=values, fill=factor(Treatment))) + 
  geom_bar(stat="identity",position = "dodge", na.rm=TRUE) + 
  labs(x="Treatment", y="No. affirmative") +
  facet_wrap(~ind) + theme_bw() + 
  theme(strip.background = element_rect(fill="#FF99BF")) +
  scale_fill_manual(values=c("#A4A4A4", "#6E6E6E", "#424242"), guide = "none")
}

marrangeGrob(facetlist[c(1:6,8:9,11,10,12,7)], nrow = 4, ncol = 3, top = NULL)
dev.print(pdf, "Results/mvabundCharacters.pdf", height = 9, width = 12)
dev.print(png, "./Results/Fig7.png", height=9, width=12, units="in", res=500)

```
##Bipartite character and treatment
```{r}
get.bip.chars<-function(bp.char){
  rownames(bp.char)<-bp.char$Group.1
  bp.char$Group.1<-NULL
  bp.g<-graph_from_incidence_matrix(as.matrix(bp.char), weighted = T)
  
  E(bp.g)$width<-E(bp.g)$weight/2
  #E(bp.g)$color<-c(rep("blue", 11), rep("green", 11), rep("orange", 11))
  E(bp.g)$color<-charcol[match(gsub(".+--", "", ends(bp.g, E(bp.g))[,2]), names(charcol))]
  
  V(bp.g)$size<-c(rep(33,3),colSums(bp.char))/2
  
  V(bp.g)$color<-charcol[match(names(V(bp.g)), names(charcol))]
  V(bp.g)$color[is.na(V(bp.g)$color)]<-"#AAAAAA"
  V(bp.g)$label.cex<-0.7
  
  return(bp.g)
}


bp.char<-aggregate(longpeach[,25:35], list(longpeach$Treatment), function(x)sum(x=="Yes"))
bp.char[,-1]<-(bp.char[,-1]*100)/(359*3)

bp.it<-aggregate(longpeach[longpeach$Site=="IT",25:35], list(longpeach$Treatment[longpeach$Site=="IT"]), function(x)sum(x=="Yes"))
bp.it[,-1]<-(bp.it[,-1]*100)/(155*3)

bp.c1<-aggregate(longpeach[longpeach$Site=="CF1",25:35], list(longpeach$Treatment[longpeach$Site=="CF1"]), function(x)sum(x=="Yes"))
bp.c1[,-1]<-(bp.c1[,-1]*100)/(103*3)

bp.c2<-aggregate(longpeach[longpeach$Site=="CF2",25:35], list(longpeach$Treatment[longpeach$Site=="CF2"]), function(x)sum(x=="Yes"))
bp.c2[,-1]<-(bp.c2[,-1]*100)/(101*3)

coord2<-readRDS("bipar.ntwk.coord.Rdata")

bp.all<-get.bip.chars(bp.char)
bp.it<-get.bip.chars(bp.it)
bp.c1<-get.bip.chars(bp.c1)
bp.c2<-get.bip.chars(bp.c2)
par(mfrow=(c(2,2)), mar=rep(0.1,4))
plot(bp.all, layout=coord2, asp=0.35); text(-0.3, 1.2,"All", font=2)
plot(bp.it, layout=coord2, asp=0.35); text(-0.3, 1.2,"Site IT", font=2)
plot(bp.c1, layout=coord2, asp=0.35); text(-0.3, 1.2,"Site CF1", font=2)
plot(bp.c2, layout=coord2, asp=0.35); text(-0.3, 1.2,"Site CF2", font=2)
dev.print(pdf, "./Results/bipartite-char.pdf", width=12, height=8)
dev.off()
```
#Putting the picture together
nation-purchase-rating-char
non-random assortment to liking?
Hypotheses:
- greater effect of char if stated as imp in buying preference
- this translates to national fx
- frequent buyers are more consistent
###Aquiescence
```{r}
#Calculate the number of 'yes' responses per country for each category
aqu<-aggregate(longpeach[,c(25:35)], list(longpeach$Country), function(x){sum(x=="Yes", na.rm = T)})
#Turn it into a %
aqu2<-as.data.frame(apply(aqu[,-1], 2, function(x)x/c(465,612)*100))
aqu2<-cbind(aqu$Group.1, stack(aqu2))
names(aqu2)<-c("Country", "Aqui", "Char")
#Calcuate % aquiescence for each country (based on no. respondents * categories)
rowSums(aqu[,-1])/c(465*11,612*11)*100
#Plot aquiescence against country
plot(aqu2$Aqui~aqu2$Country)
#Test it
qqnorm(aqu2$Aqui);qqline(aqu2$Aqui)
aqu.test<-dunn.test(aqu2$Aqui, aqu2$Country)
```
###For each character, calculate the difference in rating when it was yes vs no
```{r}
#Create a list of characters, mean rating they were when yes and no for each respondent, and the difference that made
char.diff<-data.frame(Respondent=unique(longpeach$Respondent))
for (j in names(longpeach)[25:35]){
  char.fx<-matrix(NA, nrow = length(unique(longpeach$Respondent)), ncol = 2, dimnames = list(unique(longpeach$Respondent), c("Yes", "No")))
  for (i in unique(longpeach$Respondent)){
    agg<-aggregate(longpeach$Rating[longpeach$Respondent==i], list(longpeach[,j][longpeach$Respondent==i]), mean)
    char.fx[i,agg$Group.1]<-agg$x
  }
  char.diff[,j]<-char.fx[,"Yes"]-char.fx[,"No"]
}
#Add in purchase characteristics
diff.fx<-cbind(char.diff, purchasedat[match(char.diff$Respondent, purchasedat$Respondent),c(2:4,10,16:18,23:24)])
#Stack the difference columns
diff.fx<-cbind(stack(diff.fx[,2:12]), diff.fx[,c(1,13:21)])
names(diff.fx)[1:2]<-c("Diff", "Char")
#Stack the purchase columns
for (i in names(diff.fx)[7:10]){
  diff.fx[,i]<-as.character(diff.fx[,i])
}
diff.fx<-cbind(stack(diff.fx[,7:10]), diff.fx[,c(1:6,11:12)])
names(diff.fx)[1:2]<-c("Imp.purch", "Purch")
diff.fx$Imp.purch<-factor(diff.fx$Imp.purch, levels = c("Yes", "No"))

#Match peach characteristics to purchase characteristics
char2purch<-matrix(c(
  "Aroma", "Scent",
  "Sweet", "Ripeness",
  "Sweet", "Taste",
  "Acid", "Taste",
  "Bitter", "Taste",
  "Astringent", "Taste",
  "Juicy", "Ripeness",
  "Juicy", "Texture",
  "Crunchy", "Texture",
  "Fibrous", "Texture",
  "Firm", "Texture",
  "Soft", "Ripeness",
  "Soft", "Texture",
  "Mealy", "Ripeness",
  "Mealy", "Texture"), 
  ncol=2, byrow = T)
colnames(char2purch)<-c("char", "purch")
```
###Plot differences
```{r}
ggplot(diff.fx[!is.na(diff.fx$Imp.purch),], aes(x=Purch, y=Diff, fill=Imp.purch)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  facet_wrap(~Char, scales = "free_x") +
  theme_bw() 

#Plot difference against country
ggplot(diff.fx, aes(x=Char, y=Diff, fill=Country)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw() 

#Plot difference against gender
ggplot(diff.fx[!is.na(diff.fx$Gender),], aes(x=Char, y=Diff, fill=Gender)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw() 

#Plot difference against frequency
ggplot(diff.fx[!is.na(diff.fx$Frequency2),], aes(x=Char, y=Diff, fill=Frequency2)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw() 

#Plot just aroma and scent
plot(Diff~Imp.purch, data = diff.fx[diff.fx$Purch=="Scent" & diff.fx$Char=="Aroma",], notch=T, xlab="Aroma important to purchase", ylab="Rating difference when aroma present", col=c("red", "blue"))
points(Diff~Imp.purch, data = diff.fx[diff.fx$Purch=="Scent" & diff.fx$Char=="Aroma",], pch=20)
abline(h=0, lty=2, xpd=FALSE)

dev.print(pdf, "Results/AromaDiff.pdf")
dev.print(png, "./Results/Fig8.png", height=7, width=7, units="in", res=500)

#Plot difference against purchase preference
par(mfrow=c(3,5))
for (i in 1:nrow(char2purch)){
  j<-char2purch[i,"char"]
  h<-char2purch[i,"purch"]
  #Plot it
  plot(char.diff[,j]~purchasedat[,h], xlab=h, ylab=paste0("Difference (", j, ")"))
  abline(0,0, lty=2)
}
par(mfrow=c(1,1))

#Model difference against purchase preference
#Can't do mvabund as each row has at least one NA
for (i in 1:nrow(char2purch)){
  j<-char2purch[i,"char"]
  h<-char2purch[i,"purch"]
  try(m.j<-cbind(Anova(glm(char.diff[,j]~purchasedat[,h] + purchasedat$Country + purchasedat$Frequency2 + purchasedat$Gender + purchasedat[,h]:purchasedat$Country + purchasedat[,h]:purchasedat$Frequency2), type = 2), rep(j, 6), rep(h, 6)))
  if(i == 1){tests<-m.j}
  else{tests<-rbind(tests, m.j)}
}
tests[tests$`Pr(>Chisq)`<0.05,]
#Adjust for multiple testing
tests$P.adj<-p.adjust(tests$`Pr(>Chisq)`, method = "BH")
tests[tests$P.adj<0.05,]

```
###mvabund
```{r}
mvperson <- manyglm(mvpeach ~ longpeach$Age + longpeach$Gender + longpeach$Frequency2 + longpeach$Country, family="binomial")
plot(mvperson)
mvperson$var.coefficients

person.aov<-anova(mvperson, p.uni="adjusted")
person.aov$table
```